What's hot and what's not:\\Windowed developer topic analysis

### 2009-06-29 lda-paper.tex
made it fit to 10 pages!

%XXX maybe fix
The documents we are analyzing are the commit log comments, i.e., the
comments that are added when revisions to the project are committed.
For each commit log comment we produce word distributions by counting
the occurrence of each word in the message, removing stop words and
normalizing the distribution by the size of message, in tokens.
% (dividing counts by the number of tokens).  
After
all messages are processed the distributions are extended to include
all words from all of the distributions.

>>>>

%XXX maybe fix
The documents we are analyzing are the commit log comments, i.e., the
comments that are added when revisions to the project are committed.
% For each commit log comment, we count the occurrence of each word in
% the message, remove stop words, and then produce word distributions
% for each message.  These distributions are then normalized by the size
% of the message, each count was divided by the total number of
% tokens. After all messages are processed the distributions are
% extended to include all words from all of the distributions.
% For each commit log comment, we count the occurrence of each word in
% the message, remove stop words, and then produce word distributions
% for each message, which are normalized (divided by) by the size
% of the message.
% After all messages are processed the distributions are
% extended to include all words from all of the distributions.
% 
%
For each commit log comment we produce word distributions by counting
the occurrence of each word in the message, removing stop words and
then normalizing the distribution by the size of message, in tokens.
% (dividing word counts by the number of tokens).  
After
all messages are processed the distributions are extended to include
all words from all of the distributions.
